---
title: "Text Mining-Resume Shortlist"
author: "Sabyasachi Mitra"
date: "February 17, 2017"
output: html_document
---
#Reuired package loaded
```{r required package, echo=TRUE}
library(rJava)
library(NLP)
library(tm)
library(openNLP)
library(RWeka)
library(SnowballC)
library(quanteda)
library(reshape2)
```

## Destination folder for corpus and working directory
```{r corpus, echo=TRUE}
setwd("e://my learning/resume parsing")
options(stringsAsFactors = FALSE)
corpus <-Corpus(DirSource("cv1"))
corpus
writeLines(as.character(corpus[[22]]))
getTransformations()
```

##Cleaning of data
```{r cleaning, echo=TRUE}
toSpace <- content_transformer(function(x, pattern) {return (gsub(pattern, " ", x))})
corpus <- tm_map(corpus, toSpace, ":")
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, toSpace, "'")
corpus <- tm_map(corpus, toSpace, "_")
corpus <- tm_map(corpus,content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, stripWhitespace)
writeLines(as.character(corpus[[1]]))
```

##Stemming of the cleared data set of resumes
```{r stem, echo=TRUE}
corpus <- tm_map(corpus,stemDocument)
writeLines(as.character(corpus[[22]]))
```

##Resume shortlisting based on desired skill, selection base on important skills
```{r shortlist, echo=TRUE}
skills <- c("java", "iit")
```

##Document term matrix build up
```{r dtm, echo=TRUE}
dt1 <- DocumentTermMatrix(corpus)
dim(dt1)
v <- as.vector(dt1[ ,skills]>=1)
dt2 <- dt1[v, ]
inspect(dt2[ ,skills])
dim(dt2)
```

##Removal of the dense sparse words as words might be repeatable, the requirement is only the skills which is presented on a particular portion of the resume
```{r sparse, echo=TRUE}
dt3 <- removeSparseTerms(dt2, sparse=0.2:1.0)
dim(dt2)
dim(dt3)
class(dt3)
```

##Finding of associate terms related to skills to check the accuracy of the code
```{r asscociate, echo=TRUE}
findAssocs(dt3, "java", 0.6)
dt3
```

##Reshaping and counting after taking subset of the desired resumes
```{r reshaping and counting, echo=TRUE}
dt4 <- as.matrix(dt3)
dt4 <- melt(dt4, value.name = "count")
dim(dt4)
a <- subset(dt4, dt4[,2] == skills)
head(a)
dim(a)
head(dt4)
```

##Saving the selected resume to a new file
```{r save, echo=TRUE}
write.csv(a, file="dtm.csv")
```

##Checking of frequency of the terms related to skills 
```{r frequency, echo=TRUE}
freq <- colSums(as.matrix(dt3))
length(freq)
ord <- order(freq,decreasing=TRUE)
freq[head(ord)]
freq[tail(ord)]
```

## Making a cluster of the names

```{r cluster, echo=TRUE}
m2 <- as.matrix(a)
dim(m2)
distMatrix <- dist(scale(dt3))
fit <- hclust(distMatrix, method="ward.D2")
par(cex=0.6, mar=c(5, 8, 4, 1))
plot(fit, xlab="", ylab="", main="", sub="", axes=FALSE)
par(cex=1)
title(xlab="Ward.D2", ylab="CV", main="Resume with skills")
axis(2)
(groups <- cutree(fit, k=4))
```
